### 2013-05-31 doc/nips2013/appendix.tex
a

>>>>

\subsection{Experiments}

Table~\ref{tab:errorsa} shows the full set of results for the mixture
model and HMM.

\begin{table}
\begin{center}
    \begin{tabular}{l | l l | l l l }
        Algorithm & $k$ & $\ell$ & Accuracy & $\Delta \hat \E[\phi(x,h)]$ & Log Likelihood \\ \hline
        & \multicolumn{2}{|c|}{Mixture model} & & & \\ \hline
        \multirow{3}{*}{EM} 
        & 3 & 2 & 0.65 (+/- 0.01) & 1.23 & -3.72 \\
        & 3 & 3 & 0.51 (+/- 0.06) & 1.81 & -4.21\\
        & 5 & 2 & 0.72 (+/- 0.07) & 1.13 & -5.21\\ \hline
        \multirow{3}{*}{Spectral} 
        & 3 & 2 & 0.80 (+/- 0.09) & 0.23 & -3.54 \\
        & 3 & 3 & 0.68 (+/- 0.10) & 1.01 & -3.76 \\
        & 5 & 2 & 0.80 (+/- 0.05) & 0.18 & -5.04 \\ \hline
        \multirow{3}{*}{Oracle} 
        & 3 & 2 & 0.80 (+/- 0.08) & 0.01& -3.54 \\
        & 3 & 3 & 0.70 (+/- 0.11) & 0.02& -3.87 \\
        & 5 & 2 & 0.80 (+/- 0.05) & 0.01& -5.03 \\ \hline
        & \multicolumn{2}{|c|}{HMM} & & & \\ \hline
        \multirow{3}{*}{EM} 
& 3 & 2 & 0.64 (+/- 0.10) & 1.71 & -4.51 \\  
& 3 & 3 & 0.42 (+/- 0.05) & 2.41 & -6.09 \\  
& 5 & 2 & 0.62 (+/- 0.09) & 1.60 & -6.47 \\  \hline
        \multirow{3}{*}{Spectral} 
& 3 & 2 & 0.67 (+/- 0.07) & 2.59 & -3.71 \\ 
& 3 & 3 & 0.45 (+/- 0.08) & 4.96 & -4.36 \\ 
& 5 & 2 & 0.64 (+/- 0.10) & 3.43 & -5.31 \\ \hline
        \multirow{3}{*}{Oracle} 
& 3 & 2 & 0.71 (+/- 0.07) & 0.39 & -4.64 \\ 
& 3 & 3 & 0.47 (+/- 0.07) & 1.53 & -5.85 \\ 
& 5 & 2 & 0.73 (+/- 0.07) & 0.39 & -6.16 \\ \hline
    \end{tabular}
    \caption{Micro-averaged results for various models, methods.}
    \label{tab:errorsa}
\end{center}
\end{table}

### 2013-05-31 doc/nips2013/factorial.tex
a

\item Group the bins into sources:
  For each source $i = 1, \dots, s$,
  chose any bin $\omega$, declare it as $v_{i1} - v_{i2}$,
  and add $\omega$ to the source.
  Let $\gamma$ be the set of $c$ such that $\omega$
  contains some difference vector $L_c - L_d$,
  and include any other bin $\omega'$ with the same $\gamma$;
  $\omega$' should correspond to $v_{i1} - v_{ia}$ for $a \ge 3$.

>>>>

\item Group the bins into sources:
  For each source $i = 1, \dots, s$,
  choose any bin $\omega$, declare it as $v_{i1} - v_{i2}$,
  and add $\omega$ to the source.
  Let $\gamma$ be the set of $c$ such that $\omega$
  contains some difference vector $L_c - L_d$,
  and include any other bin $\omega'$ with the same $\gamma$;
  $\omega$' should correspond to $v_{i1} - v_{ia}$ for $a \ge 3$.
